Spfy: an integrated graph database for real-time prediction of Escherichia coli phenotypes and downstream comparative analyses

### 2018-03-01 paper-webserver.tex
EDIT: how Spfys graph struct enables broader analyses

PATRIC \cite{wattam2016improvements} adds support for comparing user-submitted genomes and pre-analyzed public data, enabling comparisons of gene annotations for user-submitted genomes against reference genomes. PATRIC indexes a NoSQL document store to comparison similar document types. Unlike PATRIC which is targeted towards comparative genomics, Spfy's graph database enables broader generic comparisons against any population groupings. For example, Spfy can compare all genomes with a particular subtype for gene annotations, source metadata for gene annotations, or any two (or more) node or attribute data.

@@

>>>>

@@

PATRIC \cite{wattam2016improvements} adds support for comparing up to nine user-submitted genomes against a reference genome, targeting various gene annotations. PATRIC indexes a NoSQL document store to compare similar document types and is beneficial for comparative genomics. Unlike PARTIC, Spfy is targeted towards statistical comparisons of any population grouping, and Spfy's graph database has no limit on the number of genomes grouped for comparison. For example, Spfy can compare all genomes with a particular subtype for gene annotations, source metadata targets for gene annotations, or any two (or more) node or attribute types as shown in \ref{fig-groupings}.

\begin{figure}[!hb]
\begin{center}
\includegraphics[width=\textwidth]{images/groupings}
\end{center}
\caption{Genomes can be grouped by any node or attribute type for comparisons, and Spfy has no upper bound for the number of genomes in a group. Different types can also be joined into a group through logical connectives AND, OR, Negation, and any data type is also a valid target. This approach can be used to compare any data regardless of source software.}
\label{fig-groupings}
\end{figure}
